Simulation Tables

### 2019-07-09 mcmc_draws_2019-07-08/mcmc_draws_NOSKEW_2019-07-02/tables.Rmd
sim 1

true_c1 <- c(beta_true_c1,omega_true_c1,alpha_true_c1,delta_true,pi_true[1])
true_c2 <- c(beta_true_c2,omega_true_c2,alpha_true_c2,delta_true,pi_true[2])
true_c3 <- c(beta_true_c3,omega_true_c3,alpha_true_c3,delta_true,pi_true[3])
est_c1 <- c(beta_est_c1,omega_est_c1,alpha_est_c1,delta_est,pi_est[1])
est_c2 <- c(beta_est_c2,omega_est_c2,alpha_est_c2,delta_est,pi_est[2])
est_c3 <- c(beta_est_c3,omega_est_c3,alpha_est_c3,delta_est,pi_est[3])

load("mcmc_draws_NOSKEW_2019-07-02/class_1_est")
load("mcmc_draws_NOSKEW_2019-07-02/class_2_est")
load("mcmc_draws_NOSKEW_2019-07-02/class_3_est")

t1 <- cbind(model_component,
            params,
            true_c1,est_c1,est_c3_noskew,
            true_c2,est_c2,est_c2_noskew,
            true_c3,est_c3,est_c1_noskew)
colnames(t1) <- c("Component",
                  "Param.",
                  "True","MSN Est. (95\\% CrI)","MN Est. (95\\% CrI) ",
                  "True","MSN Est. (95\\% CrI)","MN Est. (95\\% CrI)",
                  "True","MSN Est. (95\\% CrI)","MN Est. (95\\% CrI)")
```

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1000, k = 4, p = 2, h = 3, r = 2. 1000 iterations were run with a burn in of 100. Missingness mechanism was MAR and P(miss) = 0. Model results for the multivariate skew normal (MSN) and multivariate normal (MN) mixtures are presented.") %>%
  kable_styling(font_size = 7) %>%
  add_header_above(c(" " = 2,"Class 1" = 3, "Class 2" = 3, "Class 3" = 3)) %>%
  group_rows(" ",1,8) %>%
  group_rows(" ",9,18) %>%
  group_rows(" ",19,22) %>%
  group_rows(" ",23,26) %>%
  group_rows(" ",27,27) %>%
  landscape()
```

>>>>

true_c1 <- c(beta_true_c1,omega_true_c1,alpha_true_c1,delta_true,pi_true[1])
true_c2 <- c(beta_true_c2,omega_true_c2,alpha_true_c2,delta_true,pi_true[2])
true_c3 <- c(beta_true_c3,omega_true_c3,alpha_true_c3,delta_true,pi_true[3])
est_c1 <- est_c1_noskew <- c(beta_est_c1,omega_est_c1,alpha_est_c1,delta_est,pi_est[1])
est_c2 <- est_c2_noskew <- c(beta_est_c2,omega_est_c2,alpha_est_c2,delta_est,pi_est[2])
est_c3 <- est_c3_noskew <- c(beta_est_c3,omega_est_c3,alpha_est_c3,delta_est,pi_est[3])

save(est_c1_noskew,file = "class_1_est")
save(est_c2_noskew,file = "class_2_est")
save(est_c3_noskew,file = "class_3_est")

t1 <- cbind(model_component,
            params,
            true_c1,est_c1,
            true_c2,est_c2,
            true_c3,est_c3)
colnames(t1) <- c("Model Component",
                  "Parameter",
                  "True","Est. (95\\% CrI)",
                  "True","Est. (95\\% CrI)",
                  "True","Est. (95\\% CrI)")
```

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1000, k = 4, p = 2, h = 3, r = 2. 1000 iterations were run with a burn in of 250. Missingness mechanism was MAR and P(miss) = 0") %>%
  kable_styling(font_size = 8) %>%
  add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
  group_rows(" ",1,8) %>%
  group_rows(" ",9,18) %>%
  group_rows(" ",19,22) %>%
  group_rows(" ",23,26) %>%
  group_rows(" ",27,27)
```

### 2019-07-09 mcmc_draws_2019-07-08/tables.Rmd
sim 1

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-07-02")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

>>>>

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-07-08")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

### 2019-07-09 mcmc_draws_2019-07-08/tables_2.Rmd
sim 1

---
title: "Simulation Tables"
author: "Carter Allen"
date: 
output: 
  pdf_document: 
    keep_tex: yes
---

@@

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-07-02/mcmc_draws_NOSKEW_2019-07-02/")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

@@

true_c1 <- c(beta_true_c1,omega_true_c1,alpha_true_c1,delta_true,pi_true[1])
true_c2 <- c(beta_true_c2,omega_true_c2,alpha_true_c2,delta_true,pi_true[2])
true_c3 <- c(beta_true_c3,omega_true_c3,alpha_true_c3,delta_true,pi_true[3])
est_c1 <- est_c1_noskew <- c(beta_est_c1,omega_est_c1,alpha_est_c1,delta_est,pi_est[1])
est_c2 <- est_c2_noskew <- c(beta_est_c2,omega_est_c2,alpha_est_c2,delta_est,pi_est[2])
est_c3 <- est_c3_noskew <- c(beta_est_c3,omega_est_c3,alpha_est_c3,delta_est,pi_est[3])

save(est_c1_noskew,file = "class_1_est")
save(est_c2_noskew,file = "class_2_est")
save(est_c3_noskew,file = "class_3_est")

@@

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1000, k = 4, p = 2, h = 3, r = 2. 1000 iterations were run with a burn in of 250. Missingness mechanism was MAR and P(miss) = 0") %>%
  kable_styling(font_size = 8) %>%
  add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
  group_rows(" ",1,8) %>%
  group_rows(" ",9,18) %>%
  group_rows(" ",19,22) %>%
  group_rows(" ",23,26) %>%
  group_rows(" ",27,27)
```

>>>>

---
title: "Simulation Tables"
author:
date: 
output: 
  pdf_document: 
    keep_tex: yes
---

@@

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-07-09")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

@@

true_c1 <- c(beta_true_c1,omega_true_c1,alpha_true_c1,delta_true,pi_true[1])
true_c2 <- c(beta_true_c2,omega_true_c2,alpha_true_c2,delta_true,pi_true[2])
true_c3 <- c(beta_true_c3,omega_true_c3,alpha_true_c3,delta_true,pi_true[3])
est_c1 <- c(beta_est_c1,omega_est_c1,alpha_est_c1,delta_est,pi_est[1])
est_c2 <- c(beta_est_c2,omega_est_c2,alpha_est_c2,delta_est,pi_est[2])
est_c3 <- c(beta_est_c3,omega_est_c3,alpha_est_c3,delta_est,pi_est[3])

@@

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1000, J = 4, p = 2, K = 3, r = 2. 1,000 iterations were run with a burn in of 0. Missingness mechanism was MAR and P(miss) = 0") %>%
  kable_styling(font_size = 8) %>%
  add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
  group_rows(" ",1,8) %>%
  group_rows(" ",9,18) %>%
  group_rows(" ",19,22) %>%
  group_rows(" ",23,26) %>%
  group_rows(" ",27,27)
```
